--- 
title: "Analisi" 
author: "livio e livio" 
params: 
#  keep: 'names(D)[grep("Nuclei_",names(D))]' 
#  population: "Condition_" 
  file_data: "datiD.Rdata" 
  eval: "TRUE" 
output: 
  html_document:  
    toc: yes 
  pdf_document:  
    toc: yes 
--- 
 
```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = FALSE,warning = FALSE) 
load(params$file_data) 
eval=eval(parse(text=params$eval)) 
source("functions.R") 
library(ggplot2) 
library(data.table) 
library(sjPlot) 
library(ggplot2) 
theme_set(theme_sjplot()) 
 
# devtools::install_github("ricardo-bion/ggradar",  
                          # dependencies = TRUE) 
# library(ggradar) 
# colori=c("red","blue","cyan","grey","orange", 
#          "green","black","yellow","violet", 
#          "darkred", "darkblue","darkgrey","darkgreen", 
#          "darkorange") 
#  
# shapes=c(1,15,17,19,18,21:50) 
 
suppressPackageStartupMessages(library(dplyr)) 
 
#D=data.table(D) 
 
``` 
 
# Inferential Analysis 
 
 
```{r} 
# library(lmerTest) 
require("MASS") 
require(multcomp) 
 
D=data.frame(D) 
 
D$Condition=apply(cbind(as.character(D$Compound), 
                        as.character(D$Concentration)), 
                  1,function(x) paste(x,collapse = ":")) 
D$Cond=factor(D$Condition)
D$Compound=factor(D$Compound) 
 
D$Grp=D$Group 
D$Cond=relevel(D$Cond,"Control:0") 
D$Cond=factor(D$Cond) 
 
contrasts(D$Plate)<- contr.sum 
# table(D$Cond,D$Group,D$Plate) 
 
if(eval){ 
  ### FIXED EFFECT 
  mod= glm.nb(Counts~Plate+Cond*Grp,data=D) 
   
   # mod=glmer.nb(Counts~Condition*Group3+(1|Column),data=D[D$Plate==1,]) 
  ngrps=nlevels(D$Grp) 
  nconds=23#*ngrps 
  base=cbind(matrix(0,nconds,4),diag(nconds)) 
  temp=rbind( 
    cbind(base,matrix(0,nconds,ngrps-1+nconds*5)), #gr=1 
    cbind(base,matrix(0,nconds,ngrps-1),diag(nconds),matrix(0,nconds,nconds*4)), #gr=2 
    cbind(base,matrix(0,nconds,ngrps-1+nconds),diag(nconds),matrix(0,nconds,nconds*3)),#gr=3 
    cbind(base,matrix(0,nconds,ngrps-1+nconds*2),diag(nconds),matrix(0,nconds,nconds*2)),#gr=4 
    cbind(base,matrix(0,nconds,ngrps-1+nconds*3),diag(nconds),matrix(0,nconds,nconds*1)),#gr=5 
    cbind(base,matrix(0,nconds,ngrps-1+nconds*4),diag(nconds),matrix(0,nconds,nconds*0)))#, 
    # cbind(matrix(0,nconds,ngrps+nconds*6),diag(nconds),matrix(0,nconds,nconds*0)))#gr=6 
   
  contr_mat=temp 
  rownames(contr_mat)= 
    names(coef(mod))[-c(1:4,28:32)] 
  rownames(contr_mat)[1:23]=paste0(rownames(contr_mat)[1:23],":Grp1:G0")   
   
   
  modc=glht(mod,contr_mat) 
  modc_mcp=summary(modc) 
   
  M=rbind( 
    c(1,1,1,rep(0,20)), 
    c(rep(0,3),rep(1,5),rep(0,15)), 
    c(rep(0,8),rep(1,5),rep(0,10)), 
    c(rep(0,13),rep(1,5),rep(0,5)), 
    c(rep(0,18),rep(1,5)) 
  ) 
 
   
  riducente=  kronecker(diag(1, 6), M) 
     
  contr_mat0=riducente%*%contr_mat 
  rownames(contr_mat0)=paste(sep="_",rep(levels(D$Compound)[-1],6),rep(levels(D$Group),each=5)) 
  modc0=glht(mod,contr_mat0) 
  modc0_mcp=summary(modc0) 
   
  save(mod,file="modelNbinom_fixed.Rdata", 
         modc, 
         modc_mcp, 
         modc0, 
         modc0_mcp) 
} else load(file="modelNbinom_fixed.Rdata") 
 
 
summary(modc0,adjusted(type="none")) 
print("POST HOC correction") 
modc0_mcp 
 
############## 
 
# car::Anova(mod) 
summary(modc,adjusted(type="none")) 
print("POST HOC correction") 
modc_mcp 
 
 
p=my_plot_results(mod) 
p#+ggtitle("All 4 plates")